Full Bredth v Specialization Study

### 2023-12-21 modeling_data/old_files/Full Bredth v Specialization Study.Rmd
moving files

# Assume non-rare bees are 'not -rare' DONE
# Remove cases where bee rarity changes across area # DONE
# Change common catagory to 'not-rare' (assumption: fowler is exhustive) # DONE
# location can be tossed due to data limitation, use broad scale east, west, central together.
# Do it at the genus level for plants

@@

### Question: For and common rare bees in the easter, western, and central united states respectively, is the specialization indicative of limited diet bredth?
```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
compare_df <- read.csv('/Users/nickbachelder/Desktop/Bee-Specialization-Modeling/modeling_data/compare_df.csv') %>% dplyr::select(-X)

>>>>

# Assume non-rare bees are 'not -rare' DONE
# Remove cases where bee rarity changes across area # DONE
# Change common catagory to 'not-rare' (assumption: fowler is exhaustive) # DONE
# location can be tossed due to data limitation, use broad scale east, west, central together.
# Do it at the genus level for plants

@@

### Question: For and common rare bees in the easter, western, and central united states respectively, is the specialization indicative of limited diet bredth?
```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
compare_df <- read.csv('modeling_data/compare_df.csv')
